\chapter{Language Development}

% Something about why one should use our language to program the agents, instead of using C# (AOL).

% Vis at vores sprog kan construere funktionerne til wargame, med færre linier kode end f.eks. C#. Vi skal
% vise at vores sprog har et formål. Hvad er fordele og ulemper ved vores sprog?
\section{Compiler language}
<<<<<<< .mine
The MASSIVE compiler is developed in the C\# language, which is because C\# is an object oriented language and therefore provides a good base to create classes and objects used in the compiler. E.g. the abstract syntax trees.\\
Java provides the same base as an object oriented language, but due to developing the GUI in C\# in Visual Studio, it is convenient to create the MASSIVE compiler in the same programming language.\newline
There were problems managing reference types in C\# though. 
Reference types are the kinds of objects that when created refer to an existing object in memory rather than creating a new instance of the object. \newline
Several bugs occurred due to difficulty in anticipating when something is a referenced type as opposed to a seperate object. \newline
It might therefor have been beneficial to develop the compiler in a language like Haskell, which uses the functional paradigm. 
This is because purely functional languages do not allow side effects in their functions, meaning that existing data is not altered. 
Haskell is one such language \cite{misc:haskell}, where new data is created and the alterations are applied to, so reference types are of no concern.=======
The MASSIVE compiler is developed in the C\# language, this is done because C\# is an object oriented language and therefore provides a good base to create classes and objects used in the compiler. E.g. the abstract syntax trees.\\
Java provides the same base as an object oriented language, but due to developing the GUI in C\# in Visual Studio, it is convenient to create the MASSIVE compiler in the same programming language.>>>>>>> .r1149
